Long-term perspectives of social inequality in mortality among adults and elderly

### 2017-07-04 article.Rmd
no reading of 'vb.rda' now

---
title: Long-term perspectives of social inequality in mortality among adults and elderly
  in northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: "28 juni 2017"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---

@@

```{r readalldata}
source("R/get.file.R")
vb0 <- get.file("vb0")
##if (file.exists("data/vb0.rda")){
##    load("data/vb0.rda")
##}else{
## Load remote data:
##   con <- url("http://capa.ddb.umu.se/data/vb0.rda")
##   load(con)
##   close(con)
##   save(vb0, file = "data/vb0.rda")
##}
vb0$hisclass[is.na(vb0$hisclass)] <- 4
vb0$hisclass <- factor(vb0$hisclass, labels = c("elite", "middle", "worker", "NA"))
##

vb <- get.file("vb")
##if (file.exists("data/vb.rda"))
##con <- url("http://capa.ddb.umu.se/data/vb.rda")
##load("data/vb.rda")
##load(con)
##close(con)
##
##con <- url("http://capa.ddb.umu.se/data/lisaold.rda")
lisaold <- get.file("lisaold")
##load("data/lisaold.rda")
##load(con)
##close(con)
##
##con <- url("http://capa.ddb.umu.se/data/loTab.rda")
##load(con)
##close(con)
loTab <- get.file("loTab")
##load("data/loTab.rda")
loTab$period <- factor(loTab$period)
##
vb0Tab <- aggregate(vb0[, c("event", "exposure")],
                   vb0[, c("sex", "age", "period", "cohort",
                          "urban", "civst", "hisclass")],
                   FUN = sum)
vb0Tab$age <- factor(vb0Tab$age)
```

>>>>

---
title: Long-term perspectives of social inequality in mortality among adults and elderly
  in northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: "28 juni 2017"
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---

@@

```{r readalldata}
source("R/get.file.R")
vb0 <- get.file("vb0")

vb0$hisclass[is.na(vb0$hisclass)] <- 4
vb0$hisclass <- factor(vb0$hisclass, labels = c("elite", "middle", "worker", "NA"))
##

## We don't need "vb", do we?
## vb <- get.file("vb")

lisaold <- get.file("lisaold")

loTab <- get.file("loTab")

loTab$period <- factor(loTab$period)
##
vb0Tab <- aggregate(vb0[, c("event", "exposure")],
                   vb0[, c("sex", "age", "period", "cohort",
                          "urban", "civst", "hisclass")],
                   FUN = sum)
vb0Tab$age <- factor(vb0Tab$age)
```
